Draft Results

### 2019-03-25 draftPrep.Rmd
Additional prepping for draft review, plus first trade proposal

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12),
         keeper = (Name %in% keepers)) %>%
  filter(!keeper) %>%
  arrange(z_sum %>% desc) %>%
  mutate(z_rank = row_number()) %>%
  select(z_rank, Name, z_sum, round, ADP, positions, display_position) -> draft_df

draft_df %>% saveRDS("data/draft_dataset.Rds")

draft_df %>%
  select(-display_position) %>%
  head(25) %>%
  kable()
```

>>>>

pitchers_draft %>%
  bind_rows(batters_draft) %>% 
  mutate(round = ceiling(ADP/12),
         keeper = (Name %in% keepers)) %>% 
  arrange(z_sum %>% desc) %>%
  mutate(z_rank = row_number()) %>%
  select(z_rank, Name, z_sum, round, ADP, positions, display_position, keeper) -> draft_df

draft_df %>% saveRDS("data/draft_dataset_with_keepers")

draft_df %>% filter(!keeper) %>% saveRDS("data/draft_dataset.Rds")

draft_df %>%
  select(-display_position, -keeper) %>%
  head(25) %>%
  kable()
```

### 2019-03-25 draftResults.Rmd
Additional prepping for draft review, plus first trade proposal

draft_results <- read_tsv("data/draftResults.tsv") %>%  
  clean_names() %>% 
  select(-mlb_team) %>%
  mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
  mutate(keeper = (player %in% keepers))

@@

# Consider preseason trades

>>>>

results <- read_tsv("data/draftResults.tsv") %>%  
  clean_names() %>% 
  mutate(name = chartr("áéóíñú", "aeoinu", player)) %>% 
  select(-mlb_team, -player) %>% 
  mutate(keeper = (name %in% keepers))

ranks <- readRDS("data/draft_dataset_with_keepers") %>% 
  clean_names() %>% 
  select(name, adp, z_sum, z_rank)

results <- results %>%
  left_join(ranks, by = "name")

@@

# Consider preseason trades
```{r}
results %>% 
  filter(grepl("Plouffe|Hebrew",team)) %>% 
  arrange(team, z_sum %>% desc) %>%
  View()
```
